Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
Eliminates :coffin: comments
closes #50

Multiple studies have been conducted to assess the effectiveness of chatbots in
higher education; among them, a comprehensive paper was presented by Smutny and
Schreiberova \cite{Smutny2020} reviewing 47 educational chatbots implemented in
Facebook Messenger, concluding that most of these chatbots were very basic and
that programmers require of more support to develop and offer tools for
improving coaching methods and student learning outcomes. Pérez and
collaborators \cite{perez2020rediscovering} attempted to categorize educational
chatbots attending to their purpose as service-oriented or
teaching-oriented. Service-oriented chatbots include those that provide service
support, such as Ask Holly \cite{meetholly} and Dina \cite{santoso2018dinus},
which respond to students' questions about enrollment and registration. Ask
L. U.  \cite{LancasterUniversity_2019} answers students' frequently asked
questions about schedules, grades, tutors, and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate breaking
the ice between new students by introducing them to each other. Ranoliya et
al. \cite{ranoliya2017chatbot} proposed a generic chatbot for university
students that is able to answer frequently asked questions. The University of
Granada deployed Elvira, a chatbot embedded in its main web page
\cite{MOREO20129} to perform the same task. In addition to being able to answer
pre-established frequent questions, it did so from the website of the University
of Granada using an inset persona, voiced by a real person, who lip-synced the
answers. However, in the case of Elvira, the emphasis was on the authenticity of
the speech-mouth and face gestures synchronization rather than making updating
answered questions simpler or more interactive for the administrative staff, or
more open to the rest of the university staff using actual messaging
platforms. In most cases, the embedded search engine was able to provide more
up-to-date and accurate answers than those provided by Elvira, which had to be
updated by hand (and not too often). It was eventually discontinued, and its
technology was not adapted to other platforms, since it did not really provide a
useful service. Its service was not tied to teaching anyway; it was more related
to directory queries and university-wide administrative questions, so even if it
is strictly an example of a chatbot in a university setting, it is not really a
chatbot that can be adopted by teachers to affect the learning outcomes, which
is the focus of this paper.

Contrarily to the mentioned chatbots that are focused on administrative tasks,
teaching-oriented chatbots are more sophisticated, as they set personalized
learning outcomes and monitor learning progress. For instance,
\cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
assistant chatbot developed on the Telegram messaging platform. In this study,
the Telegram platform was chosen because it is easy to use, students are
familiar with its features, and it enables them to exchange messages in
different formats (text, audio and video) \cite{fernoagua2018intelligent}. In
addition, Telegram can operate on all devices and operating systems. The
``eduAssistant'' chatbot acts as an automatic agent in the
teacher-content-student relationship, providing real-time feedback loops and a
personalized learning experience relevant to the students' acquired skills and
knowledge. Using this chatbot, educators can create interactive instances in
their lectures where they pose questions to their students and the chatbot
assists those who need further help by giving them more hints and reporting it
to the educator's dashboard \cite{fernoagua2018intelligent}. This could help
educators identify students who need more attention and provide them with more
educational resources relevant to their academic
achievement.

@@

Next, we will describe the methodology we employed to gather teachers' perspectives.

>>>>

Several studies to evaluate chatbots in higher education have been conducted. For
instance, a comprehensive study was presented by Smutny and Schreiberova
\cite{Smutny2020} reviewing 47 educational chatbots implemented in Facebook
Messenger, concluding that most of these chatbots were very basic and that programmers require of more support to develop and 
offer tools for improving coaching methods and students learning. Pérez and collaborators
\cite{perez2020rediscovering} attempted to categorize educational chatbots attending to their purpose 
as service-oriented or teaching-oriented. Service-oriented chatbots
include those that provide service support, such as Ask Holly
\cite{meetholly} and Dina \cite{santoso2018dinus}, which respond to
students' questions about enrollment and registration. Ask L. U.
\cite{LancasterUniversity_2019} answers students' frequently asked questions
about schedules, grades, tutors, and societies. LISA \cite{dibitonto2018chatbot}
and Differ \cite{differ.chat} facilitate breaking the ice between new students
by introducing them to each other. Ranoliya et al. \cite{ranoliya2017chatbot}
proposed a generic chatbot for university students that is able to answer 
frequently asked questions. The University of Granada deployed
Elvira, a chatbot embedded in its main web page \cite{MOREO20129} to perform the same task. In addition to being able
to answer pre-established frequent questions, it did so from the website of
the University of Granada using an inset persona, voiced by a real person, who
lip-synced the answers. However, in the case of Elvira, the emphasis was on the
authenticity of the speech-mouth and face gestures synchronization rather than making updating
answered questions simpler or more interactive for the administrative staff, or more open to the rest of the university staff using actual messaging platforms. In
most cases, the embedded search engine was able to provide more up-to-date
and accurate answers than those provided by Elvira, which had to be updated
by hand (and not too often). It was eventually discontinued, and its technology was not adapted to other platforms, since it did not really provide a useful service. Its service was not tied to teaching anyway; it was more related to directory queries and university-wide administrative questions, so even if it is strictly an example of a chatbot in a university setting, it is not really a chatbot that can be adopted by teachers to affect the learning outcomes, which is the focus of this paper.

Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
set personalized learning outcomes and monitor learning progress. For instance,
\cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
assistant chatbot developed on the Telegram messaging platform. In this study,
the Telegram platform was chosen because it is easy to use, students are familiar
with its features, and it enables them to exchange messages in different formats
(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
can operate on all devices and operating systems. The ``eduAssistant'' chatbot
acts as an automatic agent in the teacher-content-student relationship, providing real-time
feedback loops and a personalized learning experience relevant to the
students' acquired skills and knowledge. Using this chatbot, educators can
create interactive instances in their lectures where they pose questions to
their students and the chatbot assists those who need further help by giving
them more hints and reporting it to the educator's dashboard
\cite{fernoagua2018intelligent}. This could help educators identify
students who need more attention and provide them with more educational resources
relevant to their academic achievement. %In addition, a recent study
%has analysed how the use of chatbots positively affected the learning outcomes
%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.

@@

We will present next the methodology we followed to find out teachers' opinions.
